---
title: "MAGEO1642_2024"
author: "GCLFRK"
date: "2024-04-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MAGEO 16 42 - Experimenting with mapping with R
## Important Sources

There are 4 main information sources for this course:
Applied spatial analysis with R or now: https://r-spatial.org/book/

geocomputaion with R <https://r.geocompx.org/>,
sf package vignette <https://r-spatial.github.io/sf/articles/sf1.html>
and the R Terra vignette <https://rspatial.org/>

# Package sf

A sf object is a data frame that includes a specific column for the geometry.
Since geometries are not a single value but a set of coordinates and a type (or more), i.e. lines, points, polygons, their specific column is actually a list.

Example with the data provided within the package


```{r nc sf}
library(sf)
nc<-st_read(system.file("shape/nc.shp", package="sf"))
nc
```


Like any dataframe, you can easily compute new columns. Example, the shape index perimeter to area
```{r nc calculate field}

nc$PARATIO<-nc$PERIMETER/nc$AREA
plot(density(nc$PARATIO))
```


```{r nc plot}
plot(nc)
plot(nc[,"PARATIO"])
plot(nc[nc$BIR74>2000,"PARATIO"])
plot(nc[,16])
plot(nc$PARATIO)
```

## Create your sf



